The \vspec{} Collection: A suite of utilities to model spectroscopic phase curves of 3D exoplanet atmospheres in the presence of stellar variability.

### 2024-08-02 src/tex/ms.tex
Add line numbers and docs urls

% Define document class
\documentclass[twocolumn]{aastex631}
\usepackage{showyourwork}
\usepackage[version=4]{mhchem}
\usepackage{listings}

@@

@@

The flow of \vspec{}'s code is broken into three parts: i) read in the configuration, ii) compute planetary spectra, and iii) compute stellar spectra.
\subsection{Configuring \vspec{}}
\label{subsec:config}

@@

Listing \ref{ls:pypsg} shows a minimal example that uses \texttt{pypsg} to make a call to PSG/GlobES. Here \texttt{pypsg} converts a GCM output from the netCDF format to a \texttt{PyGCM}, which, along with data model classes like \texttt{Target} and \texttt{Observatory}, is used as an argument to construct a \texttt{PyConfig} class instance. This configuration object is then passed to an \texttt{APICall} instance. When the API call is made, the contents of the \texttt{PyConfig} are included in the body of the POST request in the \texttt{file} field. PSG reads this the same as it would if we had written those contents to a file \texttt{config.txt} and passed the \texttt{--data-urlencode file@config.txt} option to \texttt{cURL}, as are the instructions in the PSG handbook \citep[pp. 162-163]{villanueva2022}.

@@

The main model class is the \texttt{Star} object, which describes bulk properties (e.g. radius, photospheric \teff, limb darkening parameters) in addition to acting as 
a container for objects representing sources of variability such as \texttt{StarSpot}, \texttt{Facula}, \texttt{StelarFlare}, and \text{Granulation}, which are described below.

>>>>

% Define document class
\documentclass[twocolumn,linenumbers]{aastex631}
\usepackage{showyourwork}
\usepackage[version=4]{mhchem}
\usepackage{listings}

@@

\newcommand{\urldocsvspec}{\url{https://vspec-collab.github.io/VSPEC/0.6.0/index.html}}
\newcommand{\urldocsvspecvsm}{\url{https://vspec-vsm.readthedocs.io/en/latest/}}
\newcommand{\urldocspypsg}{\url{https://tedjohnson12.github.io/pypsg/}}
\newcommand{\urldocsgridpolator}{\url{https://vspec-collab.github.io/GridPolator/}}

@@

The flow of \vspec{}'s code is broken into three parts: i) read in the configuration, ii) compute planetary spectra, and iii) compute stellar spectra. Detailed API documentation, configuration parameter descriptions, and examples can be found on the \vspec{} documentation page\footnote{\urldocsvspec}.
\subsection{Configuring \vspec{}}
\label{subsec:config}

@@

Listing \ref{ls:pypsg} shows a minimal example that uses \texttt{pypsg} to make a call to PSG/GlobES. Here \texttt{pypsg} converts a GCM output from the netCDF format to a \texttt{PyGCM}, which, along with data model classes like \texttt{Target} and \texttt{Observatory}, is used as an argument to construct a \texttt{PyConfig} class instance. This configuration object is then passed to an \texttt{APICall} instance. When the API call is made, the contents of the \texttt{PyConfig} are included in the body of the POST request in the \texttt{file} field. PSG reads this the same as it would if we had written those contents to a file \texttt{config.txt} and passed the \texttt{--data-urlencode file@config.txt} option to \texttt{cURL}, as are the instructions in the PSG handbook \citep[pp. 162-163]{villanueva2022}. More details on use of this library including its API and examples can be found on the \texttt{pypsg} documentation page\footnote{\urldocspypsg}.

@@

The main model class is the \texttt{Star} object, which describes bulk properties (e.g. radius, photospheric \teff, limb darkening parameters) in addition to acting as 
a container for objects representing sources of variability such as \texttt{StarSpot}, \texttt{Facula}, \texttt{StelarFlare}, and \text{Granulation}, which are described below. For a complete description of the code, including examples, see the \texttt{vspec-vsm} documentation page\footnote{\urldocsvspecvsm}.
